Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species

### 2015-10-09 docs/ms_sageAbundance.Rmd
updates ms figures

```{r figure_1,dependson="plot-options", fig.cap="Percent cover in space and time for our study area in southwestern Wyoming.", eval=T}
library(png)
library(grid)
img <- readPNG("../results/all_years_percCover.png")
grid.raster(img)
```

@@

```{r figure_3,dependson="plot-options", fig.cap="Standardized percent cover showing the general spatial structure of above and below average pixels in the data (top panel) compared to the mean posterior estimate of the spatial field, $\\eta$ (bottom panel).", eval=T}
library(png)
library(grid)
img <- readPNG("../results/spatialfield.png")
grid.raster(img)
```

@@

```{r figure_5,dependson="plot-options", fig.cap="Histograms of projected equilibrium cover from simulations using observed climate (orange) and average observed percent cover (black).", eval=T}
library(png)
library(grid)
img <- readPNG("../results/obs_pred_hist.png")
grid.raster(img)
```

@@

```{r figure_7,dependson="plot-options", fig.cap="Estimated kernel densities for current and projected sagebrush cover across space and simulation time.", eval=T}
library(png)
library(grid)
img <- readPNG("../results/clim_change_densities.png")
grid.raster(img)
```

>>>>

```{r figure_1,dependson="plot-options", fig.cap="Percent cover in space and time for our study area in southwestern Wyoming.", eval=F}
library(png)
library(grid)
img <- readPNG("../results/all_years_percCover.png")
grid.raster(img)
```

@@

```{r figure_3,dependson="plot-options", fig.cap="Standardized percent cover showing the general spatial structure of above and below average pixels in the data (top panel) compared to the mean posterior estimate of the spatial field, $\\eta$ (bottom panel).", eval=F}
library(png)
library(grid)
img <- readPNG("../results/spatialfield.png")
grid.raster(img)
```

@@

```{r figure_5,dependson="plot-options", fig.cap="Histograms of projected equilibrium cover from simulations using observed climate (orange) and average observed percent cover (black).", eval=F}
library(png)
library(grid)
img <- readPNG("../results/obs_pred_hist.png")
grid.raster(img)
```

@@

```{r figure_7,dependson="plot-options", fig.cap="Estimated kernel densities for current and projected sagebrush cover across space and simulation time.", eval=F}
library(png)
library(grid)
img <- readPNG("../results/clim_change_densities.png")
grid.raster(img)
```

```{r figure_8,dependson="plot-options", fig.cap="Model forecasts under future climate for three IPCC emissions scenarios. Shaded regions show 90/% quantiles for simulations conducted using different sets of parameters from the MCMC output. Lines show mean trajectories.", eval=T}
library(png)
library(grid)
img <- readPNG("../results/temporal_forecast.png")
grid.raster(img)
```
